Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2024-04-18 manuscript/manuscript.qmd
Use tinytable for all manuscript tables

```{r tbl-data-sources}
#| tbl-cap: Sources for outcomes and explanatory variables
#| include: true
#| echo: false
tribble(
  ~`Outcome variables`,                        ~Description,                                                        ~Frequency,  ~Source,
  "Emergency public health measures",          "Binary indicator",                                                  "Weekly",    "Oxford COVID-19 Government Response Tracker",
  "Human rights and policy outcomes",          "Ordered categories for the severity of abuses",                     "Quarterly", "Varieties of Democracy PanDem",
  "ICCPR derogation",                          "Binary indicator",                                                  "Weekly",    "UN Treaty Collection",
  "New and cumulative COVID deaths and cases", "Counts",                                                            "Weekly",    "World Health Organization",
  "Past ICCPR derogation or action",           "Binary indicator",                                                  "Weekly",    "UN Treaty Collection",
  "Rule of law index",                         "0–1; higher values represent greater respect for rule of law",      "Annual",    "Varieties of Democracy",
  "Civil liberties index",                     "0–1; higher values represent greater respect for civil liberties",  "Annual",    "Varieties of Democracy",
  "Core civil society index",                  "0–1; higher values represent better environment for civil society", "Annual",    "Varieties of Democracy"
) %>% 
  kbl(booktabs = TRUE, linesep = "\\addlinespace[0.5em]") %>% 
  kable_styling(font_size = ifelse(fmt_out == "latex", 8.5, NA)) %>% 
  pack_rows(index = c(" " = 2, "Primary explanatory variable" = 1, "Secondary explanatory variables" = 5),
            indent = FALSE) %>% 
  column_spec(c(1, 2, 4), width = "0.25\\\\textwidth") %>% 
  column_spec(3, width = "0.1\\\\textwidth")
```

@@

\begingroup\footnotesize

\renewcommand*{\arraystretch}{1.75}

::: {.content-visible when-profile="ms"}
\singlespacing
:::

| General question                           | Outcomes                                                                                                                                  | Main explanatory variable  | Other explanatory variables                                                                                                                                              |
|-----------------|-----------------|-----------------|---------------------|
| Derogations and emergency measures (H~1~)  | Cancelling public events, Gathering restrictions, Close public transit, Restrictions on internal movement, Limits on international travel | ICCPR derogation in effect | New and cumulative COVID cases, new and cumulative COVID deaths, prior ICCPR derogations and actions                                                                     |
| Derogations and human rights (H~2~)        | Discriminatory policy, Violations of non-derogable rights, No time limit measures, Abusive enforcement                                    | ICCPR derogation in effect | New and cumulative COVID cases, new and cumulative COVID deaths, prior ICCPR derogations and actions, rule of law index, civil liberties index, core civil society index |

: Overview of outcomes and explanatory variables included in models {#tbl-vars}

\endgroup

>>>>

```{r tbl-data-sources}
#| tbl-cap: Sources for outcomes and explanatory variables
#| include: true
#| echo: false
tribble(
  ~`Variable`,                                 ~Description,                                                        ~Frequency,  ~Source,
  "Emergency public health measures",          "Binary indicator",                                                  "Weekly",    "Oxford COVID-19 Government Response Tracker",
  "Human rights and policy outcomes",          "Ordered categories for the severity of abuses",                     "Quarterly", "Varieties of Democracy PanDem",
  "ICCPR derogation",                          "Binary indicator",                                                  "Weekly",    "UN Treaty Collection",
  "New and cumulative COVID deaths and cases", "Counts",                                                            "Weekly",    "World Health Organization",
  "Past ICCPR derogation or action",           "Binary indicator",                                                  "Weekly",    "UN Treaty Collection",
  "Rule of law index",                         "0–1; higher values represent greater respect for rule of law",      "Annual",    "Varieties of Democracy",
  "Civil liberties index",                     "0–1; higher values represent greater respect for civil liberties",  "Annual",    "Varieties of Democracy",
  "Core civil society index",                  "0–1; higher values represent better environment for civil society", "Annual",    "Varieties of Democracy"
) %>% 
  tt(width = c(0.3, 0.3, 0.1, 0.3)) %>% 
  group_tt(i = list(
    "Outcome variables" = 1,
    "Primary explanatory variable" = 3,
    "Secondary explanatory variables" = 4
  ), indent = 0) %>% 
  style_tt(j = 1:4, align = "l") %>% 
  style_tt(i = c(1, 4, 6), bold = TRUE, background = "#e6e6e6", align = "c") %>% 
  style_tt(
    bootstrap_class = "table table-sm table-striped",
    tabularray_inner = "rowsep=1pt, cells={font=\\footnotesize}, row{4,6}={belowsep+=2em}"
  )
```

@@

```{r tbl-vars}
#| tbl-cap: Overview of outcomes and explanatory variables included in models
#| include: true
#| echo: false
tibble(
  `General question` = c(
    "Derogations and emergency measures (H~1~)",
    "Derogations and human rights (H~2~)"
  ),
  Outcomes = c(
    "Cancelling public events; Gathering restrictions; Close public transit; Restrictions on internal movement; Limits on international travel",
    "Discriminatory policy; Violations of non-derogable rights; No time limit measures; Abusive enforcement"
  ),
  `Main explanatory variable` = c(
    "ICCPR derogation in effect", 
    "ICCPR derogation in effect"
  ),
  `Other explanatory variables` = c(
    "New and cumulative COVID cases; New and cumulative COVID deaths; Prior ICCPR derogations and actions",
    "New and cumulative COVID cases; New and cumulative COVID deaths; Prior ICCPR derogations and actions; Rule of law index; Civil liberties index; Core civil society index"
  )
) %>% 
  tt(width = c(0.2, 0.3, 0.2, 0.3)) %>% 
  style_tt(j = 1:4, align = "l") %>% 
  format_tt(j = 1:2, markdown = TRUE) %>% 
  style_tt(
    bootstrap_class = "table table-sm table-striped",
    tabularray_inner = "rowsep=1pt, cells={font=\\footnotesize}, row{1}={valign=b}"
  )
```
